\malg: a novel interest management algorithm for distributed simulations of MMOGs

### 2008-05-08 trunk/textos/dsrt/engaoi.tex

% :: OLD ABSTRACT ::
Traditionally, a central server is utilized to provide support to MMOGs (massively multiplayer online games), where the number of participants is in the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, in order to minimize the maintenance cost of its infrastructure, but critical questions remain. Examples of the problems relative to peer-to-peer MMOG support systems are: vulnerability to cheating, overload of the upload links of the peers and difficulty to maintain consistency of the simulation among the participants. In this work, it is proposed the utilization of geographically distributed lower-cost nodes, working as a distributed game server. The distribution model and some related works are also presented. To address the communication cost imposed to the servers, we specify the \malg\ algorithm, which is a novel refinement to the area of interest technique, significantly reducing the necessary bandwidth. Simulations have been made with ns-2 and their results demonstrate that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.

>>>>

% :: OLD ABSTRACT ::
Traditionally, a central server is utilized to provide support to MMOGs (massively multiplayer online games), where the number of participants is in the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, in order to minimize the maintenance cost of its infrastructure, but critical questions remain. Examples of the problems relative to peer-to-peer MMOG support systems are: vulnerability to cheating, overload of the upload links of the peers and difficulty to maintain consistency of the simulation among the participants. In this work, it is proposed the utilization of geographically distributed lower-cost nodes, working as a distributed game server. The distribution model and some related works are also presented. To address the communication cost imposed to the servers, we specify the \malg\ algorithm, which is a novel refinement of the area of interest technique, significantly reducing the necessary bandwidth. Simulations have been made with ns-2 and their results demonstrate that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.
